Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-01-29 numerical-amr.tex
Adding a vector graphics version of the W-cycle figure.

\begin{figure}
\begin{center}
\includegraphics[width=0.6\textwidth]{figures/wcycle.eps}
\end{center}
\caption{\emph{Left:}  Example of a simple, distributed AMR hierarchy showing real and ghost grids.
\emph{Right:}  Example 2D \enzo\ grid showing real and ghost zones, as 
needed for the PPM hydro stencil. }
\label{fig:wcycle}
\end{figure}

>>>>

\begin{figure}
\begin{center}
%\includegraphics[width=0.6\textwidth]{figures/wcycle.eps}
\includegraphics[width=0.6\textwidth]{figures/timestepping.eps}
\end{center}
\caption{\emph{Left:} Example of the timesteps on a 2-level AMR
  hierarchy.  Enzo does not restrict the timesteps on the finer levels
  to be a factor of $1/2^n$ smaller.  \emph{Right:} The order in which
  the AMR grids are evaulated on each level.}
\label{fig:wcycle}
\end{figure}
